---
title: "intro"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{intro}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

I really like the colour choice in the [seaborn plotting library for python](https://github.com/mwaskom/seaborn) but I use ggplot2, so I created ggplot2 palettes with those colours. I copied the colour choice directly, so thank you to [Michael Waskom](https://github.com/mwaskom) for creating them with an open license.

Using them is simple.

Install from github if necessary


```{r, eval = FALSE}
install.packages("remotes")
remotes::install_github("chr1swallace/seaborn_pal")
```

Then use in place of other scale_fill / scale_colour functions for discrete aesthetics (ie factors).

```{r}
library(ggplot2)
library(seaborn)
ggplot(data.frame(x=1:5,y=1:5,fill=factor(1:5)), aes(x=x,y=y,fill=fill)) +
geom_tile()

ggplot(data.frame(x=1:5,y=1:5,fill=factor(1:5)), aes(x=x,y=y,fill=fill)) +
geom_tile() +
scale_fill_seaborn()

ggplot(data.frame(x=1:5,y=1:5,fill=factor(1:5)), aes(x=x,y=y,fill=fill)) +
geom_tile() +
scale_fill_seaborn(palette="dark6",direction=-1)
```

The full range of colours is
```{r}
show_seaborn()
```

